Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
Fixes

To prove the fourth property, we need to upper bound the norm of $p$.
Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
$$
\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
$$
Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
Then,
\begingroup
\allowdisplaybreaks
\begin{align*}
\norm{g_i}^2
& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 \qquad \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} \qquad \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} \qquad \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
& \le \left(8(1+\sqrt{2})^2 s \right)^s \quad \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
& \le \left(47 s \right)^s \; .
\end{align*}
\endgroup
Finally,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
\end{align*}
We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
Since $r,s \ge 1$,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
& = 2^r \left(47 rs \right)^{rs/2} \\
& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
& \le \left(188 rs \right)^{rs/2} \; .
\end{align*}
Substituting for $r$ and $s$ finishes the proof.

>>>>

To prove the fourth property, we need to upper bound the norm of $p$.
Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
$$
\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
$$
Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
Then,
\begingroup
\allowdisplaybreaks
\begin{align*}
\norm{g_i}^2
& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 \quad \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} \quad \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} \quad \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
& \le \left(8(1+\sqrt{2})^2 s \right)^s
& \le \left(47 s \right)^s \; .
\end{align*}
\endgroup
where we used that $s+1 \le 2^s$ for any non-negative integer $s$.
Finally,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
\end{align*}
We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
Since $r,s \ge 1$,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
& = 2^r \left(47 rs \right)^{rs/2} \\
& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
& \le \left(188 rs \right)^{rs/2} \; .
\end{align*}
Substituting for $r$ and $s$ finishes the proof.

### 2019-01-22 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}.
For simplicity, we assume $(x_t, y_t)\in\mathbb{R}^{d}\times [K]$ in this section.
As the name suggests, ignorant algorithms ignore the examples on which they make mistakes.
This assumption seems strong, but as we will explain below, it is actually natural,
and several recently proposed bandit classification algorithms that achieve the $\sqrt{T}$-regret bound belong to this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017}, OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}.
We will see that under the $\gamma$-weak linearly separability assumption,
if a bandit classification algorithm wants to achieve a mistake bound better than $\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the feature dimension, it must perform some meaningful update when it makes a mistake.

The ignorant algorithm is formally defined as follows.
\begin{definition} \label{definition:ignorant-algorithm}
    A bandit classification algorithm $\mathcal{A}$ is ignorant if for all $t\in[T]$,
    $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is jointly determined by
    \begin{enumerate}
        \item $x_t$
        \item $H_t\triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
        where $1 \leq \tau_1<\ldots <\tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
        are the rounds in which the algorithm predicts correctly (that is,
        $\{\tau_1, \ldots, \tau_{n_t}\} = \{1\leq \tau<t: \widehat y_\tau=y_\tau\}$).
    \end{enumerate}
    We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote the distribution $\widehat y_t$ is drawn from. Note that we let the current feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on $x_t$. Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is only determined by $H_t$.
\end{definition}

@@

The following theorem states the mistake lower bound for ignorant algorithms.
\begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
\label{theorem:ignorant_lower_bound}
    Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm.
    There exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2), \ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$,
    such that $\forall t\in[T], \|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly separable,
    and the expected number of mistakes made by $\mathcal{A}$ is lower bounded as
    \begin{align*}
        \Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right] \geq \frac{1}{10}\min\left\{\sqrt{T},
        \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\}.
    \end{align*}
\end{theorem}
Before proving the theorem, we need the following lemma.
\begin{lemma}
\label{lem:embed_d_gamma}
Let $\gamma \in (0,\frac 1 {160})$.
There exists vectors $v_1, \ldots, v_N, u_1, \ldots, u_N\in \mathbb{R}^d$, where $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$, such that:
$\| v_i \|_2 \leq 1$, $\| u_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ u_i \cdot v_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long-1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$, $\|v_i\| \leq 1$ and $\|u_i\| \leq 1$. In addition,
\[ u_i \cdot v_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
\end{proof}

@@

}
\end{algorithmic}
\end{algorithm}
For this strategy, we prove the mistake lower bound of any ignorant algorithm.
Define the indicators
\begin{align*}
A_t &= \indicator{\forall \tau\leq t, p_\tau(1|x_\tau)<1-q_0} \\
B_t &= \indicator{\exists \tau\leq t, p_\tau(1|x_\tau)\geq 1-q_0
 \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
\end{align*}
Then we have
\begin{align}
    \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right]
    &\geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
    & = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
    \label{eqn:mistake_lower_bound_temp}
\end{align}
where in the first inequality we use $A_t+B_t\leq 1$;
in the equality, we use  $B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition;
in the last inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$.
Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \geq 1-q_0 \}$ (if such $\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let $T_1=\min\{T,N\}+1$).
Then $A_t=1$ for all $t\leq T_1-1$.

Note that $B_{T_1}=1$, and for $t\geq T_1$ we have $\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t|B_t=1]=\Pr[\widehat y_t=2|B_t=1]\leq q_0$ because the algorithm is ignorant. Thus the second term in \eqref{eqn:mistake_lower_bound_temp} can be calculated as

\begin{align*}
    \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right]\geq \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right]
    = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right].
\end{align*}
Combining \eqref{eqn:mistake_lower_bound_temp} and the above inequalities, we get
\begin{align}
    \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right]\geq \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right]. \label{eqn:mistake_lower_bound_temp2}
\end{align}
In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of \eqref{eqn:mistake_lower_bound_temp2} is lower bounded by $\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case $T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
\begin{align*}
    \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right)= \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right)\geq \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right)\geq \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\}.
\end{align*}
Combining both cases concludes the proof.
\end{proof}

>>>>

In this section, we prove a mistake lower bound for a family of algorithms
called \textit{ignorant algorithms}. Ignorant algorithms ignore the examples on
which they make mistakes. As an example, \textsc{Nearest-Neighbor Algorithm}
(Algorithm~\ref{algorithm:nearest-neighbor}) presented in
Appendix~\ref{section:nearest-neighbor-algorithm} is an ingnorant algorithm.
This assumption seems strong, but as we will explain below, it is actually
natural, and several recently proposed bandit classification algorithms that
achieve the $\sqrt{T}$-regret bound belong to this family, e.g.,
SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. We will see that under the
$\gamma$-weak linearly separability assumption, if a bandit classification
algorithm wants to achieve a mistake bound better than
$\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the
feature dimension, it must perform some meaningful update when it makes a
mistake.

The ignorant algorithm is formally defined as follows.
\begin{definition} \label{definition:ignorant-algorithm}
A bandit classification algorithm $\mathcal{A}$ is ignorant if for all
$t\in[T]$, $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is
jointly determined by
\begin{enumerate}
\item $x_t$
\item $H_t\triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
where $1 \leq \tau_1 < \dots < \tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
are the rounds in which the algorithm predicts correctly (that is,
$\{\tau_1, \ldots, \tau_{n_t}\} = \{1 \le \tau < t ~:~ \widehat y_\tau=y_\tau\}$).
\end{enumerate}
We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote
the distribution $\widehat y_t$ is drawn from. Note that we let the current
feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on
$x_t$. Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is
only determined by $H_t$.
\end{definition}

@@

The following theorem states the mistake lower bound for ignorant algorithms.

\begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
\label{theorem:ignorant_lower_bound}
Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm. There
exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2),
\ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$, such that $\forall t\in[T],
\|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly
separable, and the expected number of mistakes made by $\mathcal{A}$ is lower
bounded as
\begin{align*}
\Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right]
\geq \frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
\end{align*}
\end{theorem}

Before proving the theorem, we need the following lemma.
\begin{lemma}
\label{lem:embed_d_gamma}
Let $\gamma \in (0,\frac 1 {160})$.
There exists vectors $v_1, \ldots, v_N, u_1, \ldots, u_N\in \mathbb{R}^d$, where $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$, such that:
$\| v_i \|_2 \leq 1$, $\| u_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ u_i \cdot v_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long-1995}, there exists a set of $N =
(\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots,
z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that $\theta(z_i, z_j) \geq
\sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in
[0,\pi]$, this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac
12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$,
$\|v_i\| \leq 1$ and $\|u_i\| \leq 1$. In addition,
$$
u_i \cdot v_j
= \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}
$$
\end{proof}

@@

}
\end{algorithmic}
\end{algorithm}
For this strategy, we prove the mistake lower bound of any ignorant algorithm.
Define the indicators
\begin{align*}
A_t &= \indicator{\forall \tau\leq t, p_\tau(1|x_\tau)<1-q_0} \\
B_t &= \indicator{\exists \tau\leq t, p_\tau(1|x_\tau)\geq 1-q_0
 \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
\end{align*}
Then we have
\begin{align}
& \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
& \qquad + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
& = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
\label{eqn:mistake_lower_bound_temp}
\end{align}
where in the first inequality we use $A_t+B_t\leq 1$; in the equality, we use
$B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$.
Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
$\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\leq T_1-1$.

Note that $B_{T_1}=1$, and for $t \ge T_1$ we have
$\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1] \le
q_0$ because the algorithm is ignorant. Thus the second term in
\eqref{eqn:mistake_lower_bound_temp} can be calculated as

\begin{align*}
& \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right] \\
& \ge \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right] \\
& = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right] \; .
\end{align*}
Combining \eqref{eqn:mistake_lower_bound_temp} and the above inequalities, we get
\begin{multline}
\label{eqn:mistake_lower_bound_temp2}
\mathbf{E} \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \ge
\\ \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right].
\end{multline}
In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of
\eqref{eqn:mistake_lower_bound_temp2} is lower bounded by
$\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case
$T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
\begin{align*}
& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right) \\
& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
& \ge \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\} \; .
\end{align*}
Combining both cases concludes the proof.
\end{proof}
